NMRlipids Databank

### 2021-09-14 Manuscript/main.tex

\documentclass[fleqn,10pt]{wlscirep}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\title{NMRlipids Databank}

@@

NMRlipids databank is a overlay databank composed of index files containing information on the location of original data and all essential information on simulations needed in further use and automatic analysis. Each simulation system is identified using the hash of original trajectory and topology file. The index files are stored in folder structure based on the identity codes of the simulations.

>>>>

\documentclass[fleqn,10pt]{wlscirep}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{graphicx}
\title{NMRlipids Databank}

@@

\begin{figure}
  \includegraphics[width=\textwidth]{figures/DataBankStructure.pdf}
  \caption{Structure of the NMRlipids databank}\label{DatabankStructure}
\end{figure}

NMRlipids databank is a overlay databank composed of files that contain all the essential information
on the molecular dynamics simulation trajectories that are listed in the databank.
The location publicly avaiable raw MD simulation data is flexible.
The NMRlipids databank files contain all the essential information on the
original data that enable wide range of applications.
%and all essential information on simulations needed in further use and automatic analysis.

Each simulation system is identified using the hash of original trajectory and topology file. The index files are stored in folder structure based on the identity codes of the simulations.
